\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{changepage}

\begin{document}

\begin{center}
  \large \textbf{Verifications Document} \\
  Team 2: Waddle, Starbuck, Shouse and Gee - CS 374 14F
\end{center}

The verification of our project will include the following procedures: \\
\begin{adjustwidth}{.75in}{}
  \begin{tabular}{|| l ||}
    \hline
    Black-box testing \\ \hline
    Module Testing \\ \hline
    Integration Testing \\ \hline
    System Testing \\ \hline
    Acceptance Testing \\ \hline
    performance Testing \\ \hline
    User Testing \\ \hline
    Status Reports \\ \hline
  \end{tabular}
\end{adjustwidth}
\vspace{.1in}

These are the ways in which we will implement the aforementioned procedures. \\

\hspace{-.5in} \textbf{Black Box Testing} \\

We will use the testing framework \textit{Cucumber} for testing all site-related functionality. \textit{Cucumber} can check for expected outputs when given an input
or set of inputs. Using \textit{Cucumber} will allow comprehensive, automated testing of our files. \\

\hspace{-.5in} \textbf{Module Testing} \\

We will give a complete module inputs and test the output with \textit{Cucumber}, using the actual classes/functionality of our final product \\

\hspace{-.5in} \textbf{Integration Testing} \\

This project will implement a bottom-up incremental testing approach, testing lower-level classes with drivers before testing against the actual
module that contains the lower-level classes, using \textit{Cucumber}. \\

\hspace{-.5in} \textbf{System Testing} \\

This project will have tests that run over the entire system, simulating input from a user and testing against the expected output. \\

\hspace{-.5in} \textbf{Acceptance Testing} \\

Our team will schedule a time with the customer to have the customer use our product and decide if it meets the criteria set out for it. \\

\hspace{-.5in} \textbf{Performance Testing} \\

Our team is reserching the possibility of testing code complexity using a php framework called \textit{PHP Depend}. We will use a built-in php method
for measuring response time from the \textit{cURL} library. \\

\hspace{-.5in} \textbf{GOMS test} \\

Our team will predict the actions a user will carry out and estimate the time to execute those, and then measure how long a user takes to complete
the task and compare that to our predictions. \\

Also, status reports are made weekly to record the work that is done each week and how the team is performing.
\end{document}
